MSE and dynamic state variable model with sigma function

### 2018-06-26 doc/MSE_MAR_18.tex
added new script for ploting, deleted old and unused files and added last figures and doc

\begin{figure}[!h]
\centering
\includegraphics[width=0.55\textwidth]{Figures/Areadynamics.eps} 
\caption{The Operating Model (OM) including the key processes in the dynamics of the fish populations and how it was mapped.}
\label{fig:stockdyn}
\end{figure}

@@

maximum age                                                            & $A$                    & 4               \\
number of areas                                                       &                            & 2               \\
number of seasons                                                   & $S$                     & 6               \\
natural mortality                                                       & $M_i$                 & 0.0001     \\
Asymptotic length                                                    &  $L_{\infty_i}$   & 50            \\
Growth rate                                                              & $K_i$                 &  0.4          \\
Length-weight conversion factor                             & $ \alpha_i$        &  0.00005   \\
Length-weight isomorphy factor                              & $\beta_i $         &   3              \\
&               \\
\textbf{Fleet dynamics}                                           &               \\ \hline   
&  \\%& & \\

@@

\begin{figure}[!ht]
\centering
\label{f:prices}
\includegraphics[width=.69\textwidth]{Figures/prices.eps} 
\caption{Lengths and prices of the species}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\label{f:distributions}
\includegraphics[width=.69\textwidth]{Figures/distributions.eps} 
\caption{Distribution of the two species over the areas as a function of age when stocks are in virgin stock status }
\end{figure}

\begin{table}[!h]
\centering
\caption{}
\label{scenarios}
\resizebox{0.8\textwidth}{!}{%
\begin{tabular}{l c c}
\hline
                                & \textbf{MP}            & \textbf{LO}                  \\ 
                                & \textit{(landings selectivity)}& \textit{(fulll avoidance of discards)}\\ \hline
& &   \\
Discarding                      & Allowed                        & Not allowed                 \\
Manager catch perception        & $C = L + D$                    &        $C = L$ ($D = 0$)    \\
Selectivity ($l_{ratio}$)       &  $ \neq 1$                     & $=1$                      \\
Yield per recruitment model     & based in $F_L$                 &       based in $F_C$          \\

&  &   \\\hline
\end{tabular}
}
\end{table}

\begin{enumerate}

\item
\textbf{MP Scenario: Landings selectivity},  under this scenario the fishery is under landings selectivity, only landings contribute to yield. Fishing mortality accounts for all catches, regardless wether these catches are landed or discarded.

\item
\textbf{LO Scenario: Fulll avoidance of discards}, this scenario contemplates the LO with landings selectivity only and fulll avoidance of discards.

\end{enumerate}

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=.69\textwidth]{Figures/figurecatches.eps} 
\caption{Caches and harvest rates- Prices of the two species are equal (a truly mixed fishery)}
\end{figure}

\begin{figure}[!ht]
\centering
\includegraphics[width=.69\textwidth]{Figures/figurecatches2.eps} 
\caption{Change in selectivity- Prices of the two species are equal (a truly mixed fishery)}
\end{figure}

\begin{figure}[!ht]
\centering
\includegraphics[width=.82\textwidth]{Figures/figureffort.eps} 
\caption{Effort- Prices of the two species are equal (a truly mixed fishery)}
\end{figure}

\begin{figure}[!ht]
\centering
\includegraphics[width=\textwidth]{Figures/figurerevenue.eps} 
\caption{Revenues- Prices of the two species are equal (a truly mixed fishery)}
\end{figure}
%---

>>>>

\begin{figure}[!h]
\centering
\includegraphics[width=0.4\textwidth]{Figures/Areadynamics.eps} 
\caption{The Operating Model (OM) including the key processes in the dynamics of the fish populations and how it was mapped.}
\label{fig:stockdyn}
\end{figure}

@@

maximum age                                                            & $A$                    & 6               \\
number of areas                                                       &                            & 2               \\
number of seasons                                                   & $S$                     & 6               \\
natural mortality                                                       & $M_i$                 & 0.0001     \\
Asymptotic length                                                    &  $L_{\infty_i}$   & 50            \\
Growth rate                                                              & $K_i$                 &  0.4          \\
Length-weight conversion factor                             & $ \alpha_i$        &  0.00005   \\
Length-weight isomorphy factor                              & $\beta_i $         &   3              \\
Migration                                                   & $D_i $         &   5\%              \\
&               \\
\textbf{Fleet dynamics}                                           &               \\ \hline   
&  \\%& & \\

@@

\begin{figure}[!ht]
\centering
\label{f:prices}
\includegraphics[width=.69\textwidth]{Figures/Prices.eps} 
\caption{Lengths and prices of the species}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\label{f:distributions}
\includegraphics[width=.69\textwidth]{Figures/Distributions.eps} 
\caption{Distribution of the two species over the areas as a function of age when stocks are in virgin stock status }
\end{figure}

%\begin{table}[!h]
%\centering
%\caption{}
%\label{scenarios}
%\resizebox{0.8\textwidth}{!}{%
%\begin{tabular}{l c c}
%\hline
%                                & \textbf{MP}            & \textbf{LO}                  \\ 
%                                & \textit{(landings selectivity)}& \textit{(fulll avoidance of discards)}\\ \hline
%& &   \\
%Discarding                      & Allowed                        & Not allowed                 \\
%Manager catch perception        & $C = L + D$                    &        $C = L$ ($D = 0$)    \\
%Selectivity ($l_{ratio}$)       &  $ \neq 1$                     & $=1$                      \\
%Yield per recruitment model     & based in $F_L$                 &       based in $F_C$          \\

%&  &   \\\hline
%\end{tabular}
%}
%\end{table}
% 
%\begin{enumerate}

%\item
%\textbf{MP Scenario: Landings selectivity},  under this scenario the fishery is under landings selectivity, only landings contribute to yield. Fishing mortality accounts for all catches, regardless wether these catches are landed or discarded.

%\item
%\textbf{LO Scenario: Fulll avoidance of discards}, this scenario contemplates the LO with landings selectivity only and fulll avoidance of discards.

%\end{enumerate}

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=\textwidth]{Figures/Catches.eps} 
\caption{Caches- Prices of the two species are equal (a truly mixed fishery)}
\end{figure}

\begin{figure}[!ht]
\centering
\includegraphics[width=\textwidth]{Figures/Yields.eps} 
\caption{Yields- Prices of the two species are equal (a truly mixed fishery)}
\end{figure}

\begin{figure}[!ht]
\centering
\includegraphics[width=\textwidth]{Figures/Selectivity.eps} 
\caption{Changes in selectivity- Prices of the two species are equal (a truly mixed fishery)}
\end{figure}

\begin{figure}[!ht]
\centering
\includegraphics[width=\textwidth]{Figures/Effort.eps} 
\caption{Effort- Prices of the two species are equal (a truly mixed fishery)}
\end{figure}

\begin{figure}[!ht]
\centering
\includegraphics[width=\textwidth]{Figures/Catchesbyarea.eps} 
\caption{Caches by area- Prices of the two species are equal (a truly mixed fishery)}
\end{figure}

\begin{figure}[!ht]
\centering
\includegraphics[width=\textwidth]{Figures/Economics.eps} 
\caption{Revenues- Prices of the two species are equal (a truly mixed fishery)}
\end{figure}
%---
